SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-08 scipy-1.0/paper.tex
Categorized Fortran packages where possible

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251} for performing Fourier transforms,
ODEPACK\cite{hindmarsh1983odepack} for solving ordinary differential equation initial value problems,
QUADPACK\cite{piessens1983quadpack} for numerical integration of one-dimensional functions,
FITPACK\cite{Dierckx:1993:CSF:151103} for curve-fitting and interpolation,
ODRPACK\cite{ODRPACK_Boggs} for orthogonal distance regression,
MINPACK\cite{osti_6997568} for minimization of linear and nonlinear equations,
ARPACK\cite{leh:sor:yan96} for solving large scale eigenvalue problems,
ALGORITHM 644\cite{Amos:1986:APP:7921.214331} for Bessel Functions, and
CDFLIB\cite{CDFLIB_site} for evaluation of cumulative density functions.

>>>>

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
QUADPACK\cite{piessens1983quadpack} and ODEPACK\cite{hindmarsh1983odepack} for numerical integration
and solution of initial value problems;
FITPACK\cite{Dierckx:1993:CSF:151103}, ODRPACK\cite{ODRPACK_Boggs}, and MINPACK\cite{osti_6997568} for
curve-fitting and least-squares minimization;
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251} for performing Fourier transforms;
ARPACK\cite{leh:sor:yan96} for solving eigenvalue problems;
ALGORITHM 644\cite{Amos:1986:APP:7921.214331} for computing Bessel Functions; and
CDFLIB\cite{CDFLIB_site} for evaluating cumulative density functions.
